---
title: "Week 2 - Project"
output: rmarkdown::github_document
---

### 1. Code for the reading in the dataset and/or processing the data
```{r, echo=TRUE}
unzip("data.zip")
data <- read.csv("activity.csv")
str(data)
```
The data has NA values in steps. Let's remove those missing values,
```{r, echo=TRUE}
Data <- na.omit(data)
str(Data)
```
### 2. Histogram of the total number of steps taken each day
```{r, echo=TRUE}
library(ggplot2)
library(dplyr)
Data.day <- group_by(Data, date)
Data.day <- summarise(Data.day, steps = sum(steps))
hist(Data.day$steps, breaks = 30, xlab = "Steps", main = "Total number of steps taken each day")
```

### 3. Mean and median number of steps taken each day
```{r, echo=TRUE}
mean(Data.day$steps)
median(Data.day$steps)
```

### 4. Time series plot of the average number of steps taken
```{r, echo=TRUE}
Data.interval <- group_by(Data, interval)
Data.interval <- summarise(Data.interval, steps = mean(steps))
ggplot(Data.interval, aes(x=interval,y=steps)) + geom_line()
```

### 5. The 5-minute interval that, on average, contains the maximum number of steps
```{r, echo=TRUE}
subset(Data.interval, steps == max(steps))
```

### 6. Code to describe and show a strategy for imputing missing data
My strategy is to use the mean of 5-minute interval to replace the missing data.
```{r, echo=TRUE}
sum(is.na(data))
impute.fun <- function(x) replace(x, is.na(x), mean(x, na.rm = TRUE))
data.complete <- (data %>% group_by(interval) %>% mutate(steps = impute.fun(steps)))
head(data.complete)
sum(is.na(data.complete))
```

### 7. Histogram of the total number of steps taken each day after missing values are imputed
```{r, echo=TRUE}
data.complete.day <- group_by(data.complete, date)
data.complete.day <- summarise(data.complete.day, steps = sum(steps))
hist(data.complete.day$steps, breaks = 30, xlab = "Steps", main = "Total number of steps taken each day after missing vaules are imputed", cex.main=0.8)
```

### 8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r, echo=TRUE}
library(lubridate)
data.complete$weekday <- weekdays(ymd(data.complete$date))
data.complete$weekend <- ifelse(data.complete$weekday == "Saturday" | data.complete$weekday == "Sunday", "Y", "N")
WW <- data.complete %>% group_by(interval, weekend) %>% summarize(mean = mean(steps))
ggplot(WW, aes(x = interval, y = mean)) + geom_line() +
    facet_grid(weekend ~.) + xlab("Interval") + ylab("Mean of Steps") +
    ggtitle("Comparison of Average Number of Steps in Each Interval")
```



